---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

Wilson et al. describe multiple good practices for computation reproducibility. One example they outline is on the topic of project organization. They suggest putting projects in their own individual directories and including text documents with the projects. They also suggest putting raw data and metadata in the results directory and including project source code in the src directory. Finally, they suggest putting compiled programs in the bin directory and naming all files based on their function or their content. In addition, they discuss the use of programs like R not only for computational analyses themselves, but also as a source of well-maintained software libraries. These can be useful to import and use in your code to eliminate duplication.


3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 
> sqrt (4^13)
[1] 8192

4) Push this homework to the GitHub repository for the homework. 





